We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-02 paper/paper.tex
+1 paragraph

We then build a multivariate normal distribution for $$

>>>>

We then build a multivariate normal distribution for the two halos and
the three variables consistent with a unidimensional normal
distribution using the vector of mean values and covariance matrix.
This means that our final covariance matrix is $6\times 6$ and takes
into account the correlations internal to a single galaxy and with its
partner.

This
